---
title: "Case 1: Fibroblast"
author: "XiChen"
date:  "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    self_contained: true
    thumbnails: true
    lightbox: true
    gallery: false
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T,results = "hide",eval = T,warning=FALSE,message=FALSE)
library(tidyverse)
sf.rds <- function(variable,vn = "viarablename"){
  dir.create(vn)
  namefile <- gsub(" ","",paste0(vn,Sys.time(),".rds"))
namefile <- gsub(":","",namefile)
print(variable)
saveRDS(variable,file = paste0(vn,"/",namefile),compress = F)
output <- paste0("文件 ",namefile,"存储在",vn,"文件夹")
  return(output)
}


```

 

> Datasource: Xi Chen, Yang Ding, Shiqi Yang, Lin Wei, Ming Chu, Hao Tang, Lei Kong, Yixin Zhou, Ge Gao. Identifying Key Cells for Fibrosis by Systematically Calling Cell Type–Phenotype Associations across Massive Heterogenous Datasets. (in submission)

This example data has been integrated in the SPARKLE (`SPARKLE::cwas.test.data`)


# Input data

Input formats : Seurat metadata


```{r,results = "axis"}


library(SPARKLE)


Fibroblast.data <-SPARKLE::cwas.test.data

knitr::kable(head(Fibroblast.data), caption = "Seurat metadata")  

sparkle.data <-   cwas.test.data <-  cwas_build_model_data(inputdata = Fibroblast.data,
                                           Sample = "Sample", Phenotype = "Phenotype",
                                           Celltype = "Celltype",Group = "Group",Subgroup = "Subgroup",
                                           Control_label="Control",
                                           Disease_label="Disease",
                                           selected_celltype = c("MTF","MYO-F")
                                           )


```

# Data exporlation (Optional)


## PCA

PCA plot for data exploration

```{r,eval = T}
cwas_pcadraw(sparkle.data) 
```


## Wilcoxon 

Wilcoxon rank sum test and plot

```{r,eval = T}

cwas_classic_comparision(sparkle.data)  

```

## Hausman_test{.tabset}

### Test for Group

```{r,results = "axis"}


df <- cwas_hausman_test_all(sparkle.data,variable = "Group")


knitr::kable(df, caption = "Hausman test")  

```


### Test for Subgroup

```{r,results = "axis"}


df2 <- cwas_hausman_test_all(sparkle.data,variable = "Subgroup")

knitr::kable(df2, caption = "Hausman test") 
```



#  Cell-phenotype association analysis

## All model calculation

```{r,include=TRUE,results = "hide"}
 

all.models <- cwas_allmodel_cal(sparkle.data)### calculation for all model


# If the above runs slowly, you can use a multi-core parallel strategy. 

# library(doParallel)
# all.models <- cwas_allmodel_cal(sparkle.data, num_cores = 4)

#The num_cores parameter specifies the number of cores you are using.

```

## Heatmap plot for all model


```{r,results = "hide"}
p <- cwas_allmodel_heatmap(all.models)# Plot all model AIC and Pvalue
```
 


## Forest plot for Best model selection

```{r,fig.height=6,fig.width=10,results = "hide"}

best.model <- cwas_autoselected_model(all.models)# Select the best model and plot


```




#  Cell-phenotype covariate analysis



```{r,fig.height=6,fig.width=10,results = "hide"}


all.model.cov <- cwas_2celltype_allmodel_cal(sparkle.data)# Select the best model and plot
cwas_allmodel_heatmap(all.model.cov)# Plot all model AIC and Pvalue
best.model.cov <- cwas_autoselected_model(all.model.cov)# Select the best model and plot


```


#  Cell-phenotype mediation analysis

```{r,fig.height=6,fig.width=10,result="hide"}

Your_interested_celltype="MTF"

all.model.med <- cwas_mediation_analysis(sparkle.data,X.cell = Your_interested_celltype,Best_model =best.model,method = "cell_mediate_cell" )# Select the best model and plot

```
 



#  Cell-phenotype moderation analysis



```{r,fig.height=6,fig.width=10,result="hide"}

all.model.mod <- cwas_moderation_analysis(sparkle.data,X.cell =Your_interested_celltype,Best_model =best.model,method = "cell_moderation_cell" )# Select the best model and plot



```



#  Moderation network plot

```{r,fig.height=18,fig.width=16,result="hide",eval=FALSE}
sparkle.data <-   cwas.test.data <-  cwas_build_model_data(inputdata = Fibroblast.data,
                                           Sample = "Sample", Phenotype = "Phenotype",
                                           Celltype = "Celltype",Group = "Group",Subgroup = "Subgroup",
                                           Control_label="Control",
                                           Disease_label="Disease"
                                           )
```


```{r,fig.height=18,fig.width=16,results = "hide"}

SPARKLE::Cell_phenotype_network_plot(sparkle.data)

```
