---
title: "Case 2: COVID19"
author: "XiChen"
date:  "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    self_contained: true
    thumbnails: true
    lightbox: true
    gallery: false
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T,results = "hide",eval = T,warning=FALSE,message=FALSE)
library(tidyverse)
sf.rds <- function(variable,vn = "viarablename"){
  dir.create(vn)
  namefile <- gsub(" ","",paste0(vn,Sys.time(),".rds"))
namefile <- gsub(":","",namefile)
print(variable)
saveRDS(variable,file = paste0(vn,"/",namefile),compress = F)
output <- paste0("文件 ",namefile,"存储在",vn,"文件夹")
  return(output)
}


```

 

>[Datasource: COVID-19 immune features revealed by a large-scale single-cell transcriptome atlas](https://www.cell.com/cell/fulltext/S0092-8674(21)00148-3)


This example data has been integrated in the SPARKLE (`SPARKLE::covid.data`)


# Input data

Input formats : Seurat metadata


```{r,results = "axis"}


library(SPARKLE)

covid.data.ratio <-SPARKLE::covid.data 

knitr::kable(head(metadata), caption = "Seurat metadata")  


sparkle.data <- cwas_build_model_data(inputdata = covid.data.ratio,Sample = "sampleID",Phenotype = "severity",Celltype ="celltype",Group ="tissue",Subgroup = "dataset",Control_label = "control",Disease_label = "severe/critical",Cellrate ="cellratio",selected_celltype = c("CD8","DC","Macro") )

```

# Data exporlation (Optional)


## PCA

PCA plot for data exploration

```{r,eval = T}
cwas_pcadraw(sparkle.data) 
```


## Wilcoxon 

Wilcoxon rank sum test and plot

```{r,eval = T}

cwas_classic_comparision(sparkle.data)  

```

## Hausman_test{.tabset}

### Test for Group

```{r,results = "axis"}


df <- cwas_hausman_test_all(sparkle.data,variable = "Group")


knitr::kable(df, caption = "Hausman test")  

```


### Test for Subgroup

```{r,results = "axis"}


df2 <- cwas_hausman_test_all(sparkle.data,variable = "Subgroup")

knitr::kable(df2, caption = "Hausman test") 
```



#  Cell-phenotype association analysis

## All model calculation

```{r,include=TRUE,results = "hide"}


all.models <- cwas_allmodel_cal(sparkle.data)

# If the above runs slowly, you can use a multi-core parallel strategy. 

# library(doParallel)
# all.models <- cwas_allmodel_cal(sparkle.data, num_cores = 4)

#The num_cores parameter specifies the number of cores you are using.

```

## Heatmap plot for all model


```{r,results = "hide"}
p <- cwas_allmodel_heatmap(all.models)# Plot all model AIC and Pvalue
```
 


## Forest plot for Best model selection

```{r,fig.height=6,fig.width=10,results = "hide"}

 
best.model <- cwas_autoselected_model(all.models)# Select the best model and plot


```




#  Cell-phenotype covariate analysis



```{r,fig.height=6,fig.width=10,results = "hide"}


all.model.cov <- cwas_2celltype_allmodel_cal(sparkle.data)# Select the best model and plot
cwas_allmodel_heatmap(all.model.cov)# Plot all model AIC and Pvalue
best.model.cov <- cwas_autoselected_model(all.model.cov)# Select the best model and plot


```


#  Cell-phenotype mediation analysis

```{r,fig.height=6,fig.width=10,result="hide"}

Your_interested_celltype="CD8"

all.model.med <- cwas_mediation_analysis(sparkle.data,X.cell = Your_interested_celltype,Best_model =best.model,method = "cell_mediate_cell" )# Select the best model and plot

```
 



#  Cell-phenotype moderation analysis



```{r,fig.height=6,fig.width=10,result="hide"}


all.model.mod <- cwas_moderation_analysis(sparkle.data,X.cell =Your_interested_celltype,Best_model =best.model,method = "cell_moderation_cell" )# Select the best model and plot



```



#  Moderation network plot

```{r,fig.height=18,fig.width=16,result="hide"}


# sparkle.data <- cwas_build_model_data(inputdata = covid.data.ratio,Sample = "sampleID",Phenotype = "severity",Celltype ="celltype",Group ="tissue",Subgroup = "dataset",Control_label = "control",Disease_label = "severe/critical",Cellrate ="cellratio",selected_celltype = c("CD8","DC","Macro") )
SPARKLE::Cell_phenotype_network_plot(sparkle.data )

```
